Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-26 ms.tex
updates to Subaru description.

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014.
Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also evaluate high resolution spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K, main-sequence star.	
\end{abstract}

@@

The host star \shStar\ has been characterized by both photometry and spectroscopy.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from \citet{morton2016falsePos} and this work.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis in terms of stellar radii, which can be combined with Kepler's third law to calculate the stellar density \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
In this section, we analyze available high resolution spectra to put new constraints on the stellar temperature and surface gravity.

@@

We evaluate the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
We list the observing log in Table \ref{}
None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).

@@

\subsection{Data Reduction}
The Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations \citep{masuda2018rvKIC1255}.
All telluric emission features and outliers are masked in this analysis to remove these components.
Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.

\subsection{Comparison to BOSZ}
The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it should be comparable to measurements without smoothing the Subaru spectra as was necessary for the HIGHRES models above.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.

@@

The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
\textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
In order for us to compare the BOSZ models and our data, we have to convolve the Subaru spectrum.
They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
For each parameter, we change the models by about 2 steps in the BOSZ grid.
For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
The errors are estimated from the standard deviation of the spectra over the night.
For now, we ignore the smoothing of the data that creates non-zero off-diagonal terms in the covariance matrix.

>>>>

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014.
Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K star.
\end{abstract}

@@

The host star \shStar\ has been characterized by both photometry and spectroscopy to better understand the system and parameters of the disintegrating planet and debris.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from \citet{morton2016falsePos} and this work.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis in terms of stellar radii, which can be combined with Kepler's third law to calculate the stellar density \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
In this section, we analyze available high resolution spectra to put new constraints on the stellar temperature and surface gravity.

@@

We evaluate the stellar parameters by examining the archival spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
An observing log of the 3 nights is summarized in Table \ref{tab:specObs}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\url{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy to assess disintegration activity preceding or following the spectra.
None of the observations was timed during a primary transit (phase = 0.0) or secondary eclipse (phase = 0.5 for a circular orbit).

@@

\subsection{Data Reduction}
For the 2015 data, we use the same spectra as in \citep{masuda2018rvKIC1255}.
All telluric emission features and outliers are masked in this analysis to remove these components.
Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
To combine the observations, we found the median spectrum for UT dates 2015 Aug 28 and 2015 Aug 29 to robustly combine the data.
This median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.

For the 2013 data, we follow the \texttt{iraf} reduction techniques from the instrument manual V2.0.0  \footnote{\url{https://www.subarutelescope.org/Observing/Instruments/HDS/}}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.

We performed wavelength calibration with a Thorium Argon reference spectrum.
The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.

\subsection{Comparison to BOSZ}
We first evaluate stellar parameters by comparing to the high resolving power ($R=100,000$) BOSZ grids of ATLAS-APOGEE ATLAS9 models \citep{bohlin2017bosz}.
Since the discrepancies in the literature are mostly differences in the surface gravity (see Table \ref{tab:stellObsParams}), we study the gravity-sensitive Mg triplet near 517 nm.
The $R=100,000$ models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/161,000 \approx 0.03 \AA$ to best match the data.
This was a smaller than one might expect from combining inverse resolving powers in quadrature, which would use an $R=75,000 $ kernel.

@@

We explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
For each parameter, we change the models by about 2 steps in the BOSZ grid.
For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
The errors are estimated from the standard deviation of the spectra over the night.
